---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# bbcRNA

The goal of bbcRNA is to facilitate RNA-seq analysis, starting from counts and 
ending with differentially expressed gene lists and enerichment analyses.

## Installation

You can install bbcRNA from [GitHub](https://github.com/vari-bbc) with:

``` r
devtools::install_github("vari-bbc/bbcRNA")

```

## The BbcSE class

The BbcSE class extends SummarizedExperiment. Additional features include:

* An aln_rates slot to hold alignment metrics for samples.
* The first two elements of the metadata slots store: 
    1. list of edgeR objects
        1. DGEList (must be first element)
        2. DGEGLM / DGEExact / DGELRT
    2. list of DESeq2 objecrs
        1. DESeqDataSet (must be first element)
        2. DESeqResults
    
```{r}
# attach the package
library(bbcRNA)

# run the BbcSE constructor without any data to show the structure of the object

BbcSE()
```
    
